Concurrent Programming with CXL

### 2020-05-21 book/paper.tex
"choose" scheduling fixed

\begin{figure}
\begin{code}
\verbatiminput{../Lock.cxl}
\end{code}
\caption{Mutual Exclusion using the \texttt{Lock} interface of the \texttt{synch} module.}
\label{fig:lockme}
\end{figure}

Locks are probably the most popular and basic form of synchronization
in concurrent programs.  For this reason, CXL has a module called
\texttt{synch} that includes support for locks.
Figure~\ref{fig:locks} shows how they are implemented, and
Figure~\ref{fig:lockme} gives an example of how they may be used.
Notice that the module completely hides the implementation of the
lock.
The \texttt{synch} module includes a variety of other useful
synchronization primitives, which will be discussed in later
chapters.

>>>>

\begin{figure}
\begin{code}
\verbatiminput{UpFixed.cxl}
\end{code}
\caption{Program of Figure~\ref{fig:inc} fixed with a lock.}
\label{fig:incfixed}
\end{figure}

Locks are probably the most popular and basic form of synchronization
in concurrent programs.  For this reason, CXL has a module called
\texttt{synch} that includes support for locks.
Figure~\ref{fig:locks} shows how they are implemented, and
Figure~\ref{fig:figinc} gives an example of how they may be used,
in this case to fix the program of Figure~\ref{fig:inc}.
Notice that the module completely hides the implementation of the
lock.
The \texttt{synch} module includes a variety of other useful
synchronization primitives, which will be discussed in later
chapters.
